DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-25 paper/overview.tex
Change figure sizes
Many of the figures were relatively small and hard to see, so the sizes
were increased.
Change section on camera latency

\begin{figure}[t]
  \centering
  \includegraphics[width=.4\textwidth]{figs/DeepPicar_platform}
  \caption{DeepPicar platform.}
  \label{fig:overview}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=.4\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 9 layers (5
    convolutional, 4 fully-connected layers), 27 million connections,
    250K parameters. The architecture is identical to the one used
    in NVIDIA's real self-driving car~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=.4\textwidth]{figs/track_new2}
  \caption{One of the custom tracks used for training/testing.}
  \label{fig:track}
\end{figure}

@@

Another issue we observed in training/testing the network, which could
affect the network performance, is camera latency. In DeepPicar's
context, the camera latency is from the time the camera
sensor observes the scene to the time the computer actually reads the
digitized image data. Unfortunately, this time can be significantly
long depending on the camera and the performance of the Pi. We
experimentally measure DeepPicar's camera latency as
follows~\footnote{We follow the method and the tool found at
  https://www.makehardware.com/2016/03/29/finding-a-low-latency-webcam/}.
First, we point the DeepPicar's camera towards a computer monitor, which is
conntected to the Raspberry Pi 3's HDMI output. We then launch a 
program that overlays the current time with the camera's preview
screen on the monitor. Then, an infinite number of time strings will be
shown on the monitor screen and the time difference between two
successive time strings represent the camera
latency. Figure~\ref{fig:camera-latency} shows the captured moniotor
screen. The measured camera latency is about 300-350 ms. This is
significantly higher than the latency of human perception, which is known
to be as fast as 13 ms~\cite{ThomasBurger2015}. Higher camera latency
could negatively affect to the control performance, because the DNN would
analyze stale scenes. In the future, we plan to identify and use
low-latency cameras.

\begin{figure}[t]
  \centering
  \includegraphics[width=.4\textwidth]{figs/camera_latency}
  \caption{Measuring DeepPicar's camera latency.}
  \label{fig:camera-latency}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=.55\textwidth]{figs/DeepPicar_platform}
  \caption{DeepPicar platform.}
  \label{fig:overview}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=.6\textwidth]{figs/architecture}
  \caption{DeepPicar's neural network architecture: 9 layers (5
    convolutional, 4 fully-connected layers), 27 million connections,
    250K parameters. The architecture is identical to the one used
    in NVIDIA's real self-driving car~\cite{Bojarski2016}.}
  \label{fig:architecture}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=.65\textwidth]{figs/track_new2}
  \caption{One of the custom tracks used for training/testing.}
  \label{fig:track}
\end{figure}

@@

Another issue we observed in training/testing the network, which could
affect the network performance, is camera latency. In DeepPicar's
context, the camera latency is from the time the camera
sensor observes the scene to the time the computer actually reads the
digitized image data. This time can be noticable depending on the camera 
used and the performance of the Pi. We experimentally measure the camera
latency and found it to be around 50-100 ms. This is higher than the 
latency of human perception, which is known to be as fast as 13 
ms~\cite{ThomasBurger2015}. Higher camera latency could negatively 
affect control performance, because the DNN would analyze stale scenes. 
In the future, we plan to identify and use low-latency cameras.
